Conversations in time: interactive visualisation to explore structured temporal data

### 2020-08-31 tsibbletalk.Rmd
added code and imgs for slicing section

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The University of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

@@

Figure \ref{fig:highlight-retail} (a) gives an overview of 152 series for the retail data using an overlaid time series plot, while Figure \ref{fig:highlight-retail} (b) presents a scatterplot, where each series is represented by a dot in the feature space (trend versus seasonal strength). The plot making of Figure \ref{fig:highlight-retail} (b) is aided with the `features()` function from \CRANpkg{feasts}, which summarises original data by each series down to various statistical features. This function along with other **tidyverts** functions is `tsibble`-aware, and outputs a table in a reduced form where each row corresponds to a series, thus graphically displayed as Figure \ref{fig:highlight-retail} (b).

```{r highlight-retail, fig.height = 3.3, fig.cap = "ToDo"}
```

@@

>>>>

---
title: "Conversations in time: interactive visualisation to explore structured temporal data"
author:
- name: Earo Wang
  affiliation: The University of Auckland
  address:
  - Department of Statistics
  - The University of Auckland
  - New Zealand
  email: earo.wang@auckland.ac.nz
- name: Dianne Cook
  affiliation: Monash University
  address:
  - Department of Econometrics and Business Statistics
  - Monash University
  - Australia
  email: dicook@monash.edu
bibliography: tsibbletalk.bib
abstract: >
  An abstract of less than 150 words.
preamble: |
  \usepackage{subfig}
output: rticles::rjournal_article
---

@@

Figure \ref{fig:highlight-retail-1} gives an overview of 152 series for the retail data using an overlaid time series plot, while Figure \ref{fig:highlight-retail-2} presents a scatterplot, where each series is represented by a dot in the feature space (trend versus seasonal strength). The plot making of Figure \ref{fig:highlight-retail-2} is aided with the `features()` function from \CRANpkg{feasts}, which summarises original data by each series down to various statistical features. This function along with other **tidyverts** functions is `tsibble`-aware, and outputs a table in a reduced form where each row corresponds to a series, thus graphically displayed as Figure \ref{fig:highlight-retail-2}.

```{r highlight-retail, fig.height = 6, out.width = ".49\\linewidth", fig.show = "hold", fig.cap = "ToDo", fig.subcap = c("1", "2"), fig.ncol = 2}
```

@@

```{r wrap-ped, fig.show = "hold", fig.cap = "ToDo", fig.subcap = c("(1)", "(2)", "(3)"), fig.ncol = 1}
include_graphics("img/wrap-0.png")
include_graphics("img/wrap-1.png")
include_graphics("img/wrap-7.png")
```

### 2020-08-31 tsibbletalk.tex
added code and imgs for slicing section

Figure \ref{fig:highlight-retail} (a) gives an overview of 152 series
for the retail data using an overlaid time series plot, while Figure
\ref{fig:highlight-retail} (b) presents a scatterplot, where each series
is represented by a dot in the feature space (trend versus seasonal
strength). The plot making of Figure \ref{fig:highlight-retail} (b) is
aided with the \texttt{features()} function from \CRANpkg{feasts}, which
summarises original data by each series down to various statistical
features. This function along with other \textbf{tidyverts} functions is
\texttt{tsibble}-aware, and outputs a table in a reduced form where each
row corresponds to a series, thus graphically displayed as Figure
\ref{fig:highlight-retail} (b).

@@

{\centering \includegraphics[width=\textwidth]{figure/highlight-retail-1}

@@

>>>>

Figure \ref{fig:highlight-retail-1} gives an overview of 152 series for
the retail data using an overlaid time series plot, while Figure
\ref{fig:highlight-retail-2} presents a scatterplot, where each series
is represented by a dot in the feature space (trend versus seasonal
strength). The plot making of Figure \ref{fig:highlight-retail-2} is
aided with the \texttt{features()} function from \CRANpkg{feasts}, which
summarises original data by each series down to various statistical
features. This function along with other \textbf{tidyverts} functions is
\texttt{tsibble}-aware, and outputs a table in a reduced form where each
row corresponds to a series, thus graphically displayed as Figure
\ref{fig:highlight-retail-2}.

@@

{\centering \subfloat[1\label{fig:highlight-retail-1}]{\includegraphics[width=.49\linewidth]{figure/highlight-retail-1} }\subfloat[2\label{fig:highlight-retail-2}]{\includegraphics[width=.49\linewidth]{figure/highlight-retail-2} }

@@

{\centering \subfloat[(1)\label{fig:wrap-ped-1}]{\includegraphics[width=\textwidth]{img/wrap-0} }\newline\subfloat[(2)\label{fig:wrap-ped-2}]{\includegraphics[width=\textwidth]{img/wrap-1} }\newline\subfloat[(3)\label{fig:wrap-ped-3}]{\includegraphics[width=\textwidth]{img/wrap-7} }

\caption[ToDo]{ToDo}\label{fig:wrap-ped}
\end{figure}
\end{Schunk}
